Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Next, we prove the second claim, i.e., $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because as mentioned $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $B_\bm{t}$ is covered by $\gbot(\bm{t})$. The fact of $h$ crossing $\gbot(\bm{t})$ indicates that the x-range of $h$ contains that of $B_\bm{t}$. Hence, either $h$ is disjoint with $B_\bm{t}$ or $h$ crosses $B_\bm{t}$. However, $h$ cannot be disjoint with $B_\bm{t}$ because as explained before $B_\bm{t}$ contains the point $h \cap v$. It thus follows that $h$ crosses $B_\bm{t}$.

\extraspacing \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle). We will show that $h \in \dcross_H(\bm{t})$, and hence $\dcross_H(\bm{t})$ cannot be empty. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as has already been argued in our proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.

@@

By the way $r'$ is defined, the bottom edge of $r'$ must be contained in $h$. Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and hence also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must contain that of $r'$ (because $h$ crosses $r'$), which in turn must contain that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. Combining this with $h \cap B_{\bm{t}}\neq \emptyset$ yields that $h$ must cross $B_\bm{t}$.

>>>>

Next, we prove the second claim, i.e., $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. It suffices to show only the former due to symmetry. To prove $h \in \dcross_H(\bm{t})$, we need to argue that $h$ crosses $\gbot(\bm{t})$ and $B_\bm{t}$. The first part, $h$ crossing $\gbot(\bm{t})$, is done because as mentioned $h$ crosses each of $r_1', ..., r_{k-2}'$, and $\gbot(\bm{t})$ is one of those rectangles. To prove that $h$ crosses $B_\bm{t}$, first note that $h \cap B_\bm{t} \ne \emptyset$ because as explained before $B_\bm{t}$ contains the point $h \cap v$. On the other hand, as $\gbot(\bm{t})$ covers $B_\bm{t}$, the fact of $h$ crossing $\gbot(\bm{t})$ indicates that the x-range of $h$ contains that of $B_\bm{t}$. Combining this with $h \cap B_\bm{t} \ne \emptyset$ shows that $h$ crosses $B_\bm{t}$.

\extraspacing \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle, contradicting the definition of $r'$). We will show that $h \in \dcross_H(\bm{t})$ and hence $\dcross_H(\bm{t}) \ne \emptyset$. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as we already know from the above proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.

@@

By the definitions of $r'$ and $h$, the bottom edge of $r'$ must be contained in $h$. Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and hence also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must contain that of $r'$ (because $h$ crosses $r'$), which in turn must contain that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. Combining this with $h \cap B_{\bm{t}}\neq \emptyset$ yields that $h$ must cross $B_\bm{t}$.
